Technique for \earlywarning\ detection of compact binary coalescence and its implication for multimessenger astronomy

### 2011-06-02 analysis.tex
fixed broken tex
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@834 ccdd05d5-56c1-461a-bf98-85f6876523b4

The planning stage begins with choosing templates that cover the space of mass
parameters with a hexagonal grid~\cite{PhysRevD.76.102004} in order to satisfy
a minimum match criterion.  This assures a user-specified, maximum loss in SNR
for signals that fall in-between the chosen templates.  Typically the minimum
match is 97\% corresponding to a maximum mismatch of 3\%.  Next, the templates
are subdivided into groups of neighbors called ``sub-banks'' that are
appropriately sized so that each bank can be efficiently handled by a single
computer.  The neighbors are chosen to have similar chirp mass, which produces
subbanks with very similar waveforms.  Dividing the mass space into smaller
sub-banks aids in the computational cost of the singular value decomposition
and is the approach considered in~\cite{Cannon:2010p10398}.  Using our
understanding of the time-frequency evolution of the templates, we choose time
slice boundaries as in \eqref{FIXME} such that all of the templates within a
sub-bank are sub-critically sampled at progressively lower sample rates.  Next,
the templates within the sub-bank are realized as \fir\ filter
coefficients.  For each time slice, the templates are downsampled to the
appropriate sample rate.  Finally, the \SVD\ is applied to each time
slice in the sub-bank in order to produce a set of orthogonal \fir\
filters and a reconstruction matrix that maps them back to the original
templates as described in \eqref{FIXME}.  The downsampled orthogonal
\fir\ filter coefficients, the reconstruction matrix, and the time slice
boundaries are all saved to disk.

@@

In the next section we present an end-to-end test of the \lloid\ algorithm
implemented in \gstlal\.

>>>>

The planning stage begins with choosing templates that cover the space of mass
parameters with a hexagonal grid~\cite{PhysRevD.76.102004} in order to satisfy
a minimum match criterion.  This assures a user-specified, maximum loss in SNR
for signals that fall in-between the chosen templates.  Typically the minimum
match is 97\% corresponding to a maximum mismatch of 3\%.  Next, the templates
are subdivided into groups of neighbors called ``sub-banks'' that are
appropriately sized so that each bank can be efficiently handled by a single
computer.  The neighbors are chosen to have similar chirp mass, which produces
subbanks with very similar waveforms.  Dividing the mass space into smaller
sub-banks aids in the computational cost of the singular value decomposition
and is the approach considered in~\cite{Cannon:2010p10398}.  Using our
understanding of the time-frequency evolution of the templates, we choose time
slice boundaries as in \eqref{FIXME} such that all of the templates within a
sub-bank are sub-critically sampled at progressively lower sample rates.  Next,
the templates within the sub-bank are realized as \fir\ filter
coefficients.  For each time slice, the templates are downsampled to the
appropriate sample rate.  Finally, the SVD is applied to each time
slice in the sub-bank in order to produce a set of orthogonal \fir\
filters and a reconstruction matrix that maps them back to the original
templates as described in \eqref{FIXME}.  The downsampled orthogonal
\fir\ filter coefficients, the reconstruction matrix, and the time slice
boundaries are all saved to disk.

@@
